Hypertension and microbiome

### 2019-03-22 articletwo.Rmd
Minor

@@

```{r save session}
save.image(file = paste0("rds/session-", now, ".Rdata"))
```

>>>>

```

```{r lactobacillus table}
allruns.unamb <- turkumetabolites::unambiguous.lmrank(dset$fr02, linear.lmrank)
allruns.sup <- turkumetabolites::pub.lmrank(allruns.unamb,  p = 0.05/330)

maaslin.lacto.max.table <- maaslin$lacto.max %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
                  beta_ci =sprintf("%.1E", Coefficient, NA),
                  p.value = sprintf("%.2f", p.adjust(P.value, method="BH"))) %>%
    merge(., names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    select(Feature, Name, beta_ci, p.value) %>%
    gather(variable, value, -Feature, -Name) %>%
    unite(temp, Name, variable) %>%
    spread(temp, value) %>%
    mutate(Feature = rename.genus(gsub("_Bacteria", "", Feature))) %>%
    arrange(Feature)

names(maaslin.lacto.max.table) <- gsub(" ", "_", names(maaslin.lacto.max.table ))

typology.tbl2 <- data.frame(col_keys = c("Feature",
                                         "Mean_arterial_pressure_beta_ci",
                                         "Mean_arterial_pressure_p.value",
                                         "Systolic_BP_beta_ci",
                                         "Systolic_BP_p.value",
                                         "Diastolic_BP_beta_ci",
                                         "Diastolic_BP_p.value",
                                         "Pulse_pressure_beta_ci",
                                         "Pulse_pressure_p.value",
                                         "Hypertension_beta_ci",
                                         "Hypertension_p.value"),
                            what = c( "",
                                     rep("MAP", 2), 
                                     rep("Systolic BP", 2), 
                                     rep("Diastolic BP", 2), 
                                     rep("Pulse pressure", 2), 
                                     rep("Hypertension", 2)),
                            measure = c("Lactobacillus", rep(c("β±SE", "p"), 5)),
                            stringsAsFactors = FALSE)

tbl2 <- flextable(data = maaslin.lacto.max.table) %>%
    set_header_df(mapping = typology.tbl2, key = "col_keys") %>%
        flextable::theme_booktabs()
writetable(doc, tbl2, number = 2, tbl2head, tbl2foot)
print(doc, target = paste0("report/articletwo-test.docx"))
```

```{r write table 2}
tbl2head <- "Lactobacilli"
tbl2foot <- ""
writetable(doc, tbl2, number = 2, tbl2head, tbl2foot)
```

@@

```{r save session}
save.image(file = paste0("session/session-", now, ".Rdata"))
```
